Symbolic music generation using Mamba architecture

### 2024-06-14 docs/paper/paper.tex
added Future work section

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Michael Shell}
%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: http://www.michaelshell.org/contact.html}
%\and
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}
\author{\IEEEauthorblockN{Jan Retkowski} \and \IEEEauthorblockN{Miłosz Łopatto} \and \IEEEauthorblockN{Jakub Stępniak}}

@@

\section{Training Setup}
TODO
\section{Experiments}
TODO
\section{Conclusions}
TODO
% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Michael Shell}
%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: http://www.michaelshell.org/contact.html}
%\and
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}
\author{\IEEEauthorblockN{Jan Retkowski} \and \IEEEauthorblockN{Miłosz Łopatto}
    \IEEEauthorblockA{\textit{Faculty of Electronics and Information Technology} \\
        \textit{Warsaw University of Technology}\\
        Warszawa, Polska \\
        TODO: emails}
    \and \IEEEauthorblockN{Jakub Stępniak}}

@@

\section{Training Setup}
TODO
\section{Experiments}
\subsection{Synthetic Data}
To first check that our training setup is correct we decided to overfit the model to synthetic data. For this purpose we generated sequence $0, 1, ..., 1999$ and trained the tried to make model generate it after receiving 0 token as imput. During the training loss  quickly approached zero. When testing the model it managed to generate the entire sequence correctly, abeit it requred tunung the generation function's parameters.

\begin{figure}[!htbp]
    \centering \includegraphics[width=\linewidth]{../assets/synth_data_train.png}
    \caption{ Loss during training on synthetic data}
    \label{fig:synth}
\end{figure}

\section{Conclusions}
TODO

\section{Future work}
While Mamba offers better performance than transformers, it comes at the cost of output quality. A promising direction for future research is to experiment with hybrid architectures that combine the strengths of both models. Examples of such architectures include \textbf{MambaFormer} \cite{mambaformer} and \textbf{Jamba} \cite{jamba}.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}
